% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[a4paper,margin=2cm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
%-------------------------
% Adapted from Aras Gungore
% https://github.com/arasgungore/arasgungore-CV
%------------------------


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\hypersetup{frenchlinks=true}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0pt}

\titleformat
  {\section}
  {
    \vspace{-4pt}\scshape\raggedright\large
  }
  {}
  {0em}
  {}
  [\color{black}\titlerule \vspace{-5pt}]

\titleformat
  {\subsection} 
  {\centering\bfseries\LARGE}
  {\thechapter} {} {} 

\titleformat
  {\subsubsection} 
  {\bfseries\large}
  {}{}{} 

\titlespacing*{\subsubsubsection}{0pt}{*0}{0pt}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{artemii-gerasimovich}{%
\section{Artemii Gerasimovich}\label{artemii-gerasimovich}}

\textbf{GitHub} \href{https://github.com/QuentinI/}{QuentinI} ·
\textbf{LinkedIn} \href{https://www.linkedin.com/in/q-ink/}{q-ink} ·
\textbf{mail}
\href{mailto:mbee@pm.me}{\href{mailto:mbee@pm.me}{\nolinkurl{mbee@pm.me}}}

\hypertarget{experience}{%
\subsection{Experience}\label{experience}}

\hypertarget{middle-rust-developer--soramitsu}{%
\subsubsection{\texorpdfstring{Middle Rust Developer @
\href{https://soramitsu.co.jp/}{Soramitsu}}{Middle Rust Developer @ Soramitsu}}\label{middle-rust-developer--soramitsu}}

\hypertarget{stack-rust-tokio-python-pyo3-nix}{%
\paragraph{Stack: Rust, tokio, Python, PyO3,
Nix}\label{stack-rust-tokio-python-pyo3-nix}}

\hypertarget{duration-apr-2022---present}{%
\paragraph{Duration: Apr. 2022 -
Present}\label{duration-apr-2022---present}}

\hypertarget{responsibilities}{%
\paragraph{Responsibilities}\label{responsibilities}}

\begin{itemize}
\tightlist
\item
  Part of Iroha 2 core team, contributing to the development of a
  distributed ledger
\item
  Maintainer of Iroha 2 python bindings
\item
  Creator and maintainer of blockchain upgrade tool for Iroha 2
\end{itemize}

\hypertarget{middle-rust-developer--kupibilet}{%
\subsubsection{\texorpdfstring{Middle Rust Developer @
\href{https://www.kupi.com/}{Kupibilet}}{Middle Rust Developer @ Kupibilet}}\label{middle-rust-developer--kupibilet}}

\hypertarget{stack-rust}{%
\paragraph{Stack: Rust}\label{stack-rust}}

\hypertarget{duration-nov-2021---apr-2022--6-mos}{%
\paragraph{Duration: Nov 2021 - Apr 2022 · 6
mos}\label{duration-nov-2021---apr-2022--6-mos}}

\hypertarget{responsibilities-1}{%
\paragraph{Responsibilities:}\label{responsibilities-1}}

\begin{itemize}
\tightlist
\item
  Integrated third-party airline API with the company\textquotesingle s
  aggregator engine
\end{itemize}

\hypertarget{rust-developer--d3-technologies-now-skyroads}{%
\subsubsection{\texorpdfstring{Rust Developer @
\href{https://skyroads.com/}{D3 Technologies (now
Skyroads)}}{Rust Developer @ D3 Technologies (now Skyroads)}}\label{rust-developer--d3-technologies-now-skyroads}}

\hypertarget{stack-rust-tokio-hyper-postgresql}{%
\paragraph{Stack: Rust, tokio, hyper,
PostgreSQL}\label{stack-rust-tokio-hyper-postgresql}}

\hypertarget{duration-apr-2021---nov-2021--8mos}{%
\paragraph{Duration: Apr 2021 - Nov 2021 ·
8mos}\label{duration-apr-2021---nov-2021--8mos}}

\hypertarget{responsibilities-2}{%
\paragraph{Responsibilities:}\label{responsibilities-2}}

\begin{itemize}
\tightlist
\item
  Developed backend applications in Rust with PostgreSQL as the database
\item
  Created tools for integrating various avionics devices
\end{itemize}

\hypertarget{embedded-software-developer--avtomatika}{%
\subsubsection{Embedded Software Developer @
Avtomatika}\label{embedded-software-developer--avtomatika}}

\hypertarget{stack-c-freertos-stm32}{%
\paragraph{Stack: C, FreeRTOS, STM32}\label{stack-c-freertos-stm32}}

\hypertarget{duration}{%
\paragraph{Duration:}\label{duration}}

\begin{itemize}
\tightlist
\item
  Dec. 2018 - Jul. 2020 (part-time) · 1y7mos
\item
  Jul. 2020 - Apr. 2021 (fulltime) · 10mos
\end{itemize}

\hypertarget{responsibilities-3}{%
\paragraph{Responsibilities:}\label{responsibilities-3}}

\begin{itemize}
\tightlist
\item
  Developed embedded firmware for an STM32 microcontroller (part of a
  larger board)
\item
  Implemented proprietary protocols on top of SDIO/UART/SPI/1-Wire
\item
  Implemented proprietary modifications to USB protocol
\item
  Patched and expanded STM HAL USB drivers to support additional device
  classes
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{technical-skills}{%
\subsection{Technical skills}\label{technical-skills}}

\hypertarget{rust}{%
\paragraph{Rust}\label{rust}}

Proficient, 4+ years of experience, 2+ years of professional experience.
Experience with async (tokio), serde, hyper. Limited experience with
procedural macros and FFI.

\hypertarget{c}{%
\paragraph{C}\label{c}}

Good, 2 years of professional experience building embedded software.

\hypertarget{python}{%
\paragraph{Python}\label{python}}

Good, some professional experiense, mostly personal use.

\hypertarget{nix}{%
\paragraph{Nix}\label{nix}}

Good, some professional experience, extensive personal use.

\hypertarget{postgresql}{%
\paragraph{(Postgre)SQL}\label{postgresql}}

Some experience in writing queries and stored procedures.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{languages}{%
\subsection{Languages}\label{languages}}

\hypertarget{russian}{%
\paragraph{Russian}\label{russian}}

fluent, native speaker.

\hypertarget{english}{%
\paragraph{English}\label{english}}

C1, experience working on English-speaking teams.

\hypertarget{german}{%
\paragraph{German}\label{german}}

A1.

\hypertarget{turkish}{%
\paragraph{Turkish}\label{turkish}}

A1.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{education}{%
\subsection{Education}\label{education}}

\textbf{BSc in Computational and Applied Mathematics (unfinished)}

2017-2020, Saint-Petersburg State University

\end{document}
